\chapter*{Acknowledgements}

The majority of this thesis is written in the first person. However, each of those I's refers to a large group of people without whom I would not have been able to complete this work. Of course, I want to thank my supervisors Silvia and Philipp first and foremost. Thank you for all of the meetings where our insightful discussions aided me in moving forward with this project. Thank you for your trust, confidence, guidance, and helpful feedback while I was writing my thesis. And, of course, for all advice and conversations throughout my PhD-hunt. I am excited to continue working with you in the coming years.

I'd also like to thank Prof. Dr. Alex de Koter, for our conversations regarding the investigated physics. Alex, thank you for your advice and valuable feedback, especially on my PhD application presentation. Furthermore, I'd like to thank Dr. Martin Heemskerk for welcoming me every time I showed up at his door with a new problem. Martin, your willingness to assist me and eagerness to find solutions together were truly motivating, especially during times that it was most needed.

The past eleven months, the MSc room had become my second home and thanks to my classmates, this isn't as bad as it sounds. Tess, Mariana, Georgia, Teressa, Maitrey and Jip thank you for the great 
atmosphere, the late afternoon drinks at Oerknal, the assistance by listening to my complains about unwilling code and the way-to-many evenings that we spent together working. Girls, thank you for reminding me that I should take small breaks during work by dragging me into conversations regarding Harry Styles or the legendary, by now, twelve-abs girl from the gym. Maitrey, your magical ability to create chocolate and pop-corn out of thin air on daily basis, was the hydrogen-fuel in this long main sequence. Special thanks to Jip for bearing with me the long Harry Styles discussions, for listening to my presentation way too many times during the PhD application period, and for the delightful and useful discussions over physics. 

Finally, I'd like to thank my family for their encouragement in my decision to study Astronomy and Astrophysics at the University of Amsterdam. Above all, I want to thank my grandfather, Adam. Despite the fact that you never received proper education, you actively supported my desire to pursue higher education from the beginning of my BSc to the end of my MSc. That is something special to me for which I will always be grateful.
