\chapter{Conclusions \& Discussion}\label{discussion}

\epigraph{Your assumptions are your windows on the world. Scrub them off every once in a while, or the light won’t come in.}{Isaac Asimov}

In this final chapter, I summarize the presented work and display my conclusions. In addition, I compare my results with previous studies and provide some estimations about the system's evolution. 

\input{Thesis/5.Discussion_Conclusions/Section_5-1}

\input{Thesis/5.Discussion_Conclusions/Section_5-2}

\input{Thesis/5.Discussion_Conclusions/Section_5-3}

\input{Thesis/5.Discussion_Conclusions/Section_5-4}





\begin{comment}
    


In this case, the angular momentum vectors of the inner binary and the inflowing gas are (almost) aligned, hence less angular momentum is required to accelerate the gas to the escape velocity. Furthermore, on the current resolution the gas drag is considerably underestimated.

Indeed, when the angular momentum vectors of the inner binary and the inflowing gas are (almost) aligned, less angular momentum needs to be transferred to speed up the gas to the escape velocity.


s.

The work is partially exploratory, as I try to test the efficiency of the method considering different internal structure for the donor star.


I use AMUSE \citep{pelupessy2013astrophysical,portegies2018astrophysical} in order to handle stellar evolution, hydrodynamics and gravity in a self-consistent way.




\section{Discussion}

In this section, I describe some crucial features of the modeling method that will assist the reader in interpreting the graphs, presented in the next sections. 
\end{comment}